%=== FRONT PART ===
%=== ABSTRCT ===

%\begin{center}
\chapter*{Abstract}
%\end{center}
\addcontentsline{toc}{chapter}{Abstract}

This thesis addresses the technical and operational challenge of integrating \textbf{Salesforce}, a non-\textbf{SAP CRM} system, with \textbf{SAP S/4HANA}, an \textbf{ERP} system used by manufacturers. Sales representatives often face inefficiencies due to the lack of access to \textbf{real-time customer information} stored in the \textbf{ERP} system, such as order details and account updates. This disconnect hinders their ability to respond promptly to customer inquiries, resulting in \textbf{operational delays}.

\vspace{0.5cm} % Add vertical spacing between paragraphs

The proposed solution employs the \textbf{SAP Business Technology Platform (BTP) Integration Suite} as middleware to enable seamless synchronization between the two systems. The integration demonstrates a scenario where a \textbf{Business Partner} in \textbf{S/4HANA} is converted into a \textbf{Salesforce Account}, ensuring that the salesperson has access to the latest customer information. This technical solution showcases how \textbf{ERP-CRM integration} can streamline \textbf{data flow}, eliminate \textbf{manual intervention}, and enhance the efficiency of \textbf{sales operations}.

\vspace{0.5cm} % Add vertical spacing between paragraphs

The thesis is structured as follows: the \textbf{business problem} is defined and contextualized, followed by a review of relevant academic and industry research. Next, the design and \textbf{technical implementation} of the integration are detailed, including a step-by-step demonstration via video. The work concludes by highlighting the significance of the integration for addressing the specific problem, without delving into broader business implications.

\vspace{0.5cm} % Add vertical spacing between paragraphs

This research focuses on the \textbf{technical aspects} of \textbf{ERP-CRM integration} and serves as a practical guide for implementing similar solutions using the \textbf{SAP BTP Integration Suite}.


\vfill % Pushes everything below it to the bottom of the page


\par
\textbf{Keywords:} Salesforce integration, SAP S/4HANA, ERP-CRM integration, SAP BTP, BTP Integration Suite, real-time data synchronization, operational efficiency, sales operations, middleware solutions, data flow automation, customer information access, technical implementation, digital transformation.

%=== END OF CHAPTER ONE ===
