%=== FRONT PART ===
%=== ACKNOWLEDGEMENT ===

%\begin{center}
\chapter*{Acknowledgement}
%\end{center}
\addcontentsline{toc}{chapter}{Acknowledgement}

\noindent
I would like to express my deepest gratitude to my thesis advisors, \textbf{Prof. Dr. Christian Leubner} and \textbf{Prof. Dr.-Ing. Klaus Posten}, for their continuous support, insightful guidance, and encouragement throughout this research. Their expertise and valuable feedback have been instrumental in shaping the direction of this thesis.

\noindent
I am also thankful to my colleagues and peers at \textit{FH Südwestfalen} for their constructive discussions and technical insights, which helped me refine my ideas and overcome challenges along the way.

\noindent
A special thanks to my employer, \textbf{Cpro Industry Projects \& Solutions GmbH}, and my contact person, \textbf{Mr. Florian Flemming}, for providing me with the necessary resources and an environment conducive to learning. Their support has significantly contributed to the practical aspects of this research.

\noindent
Lastly, I am deeply grateful to my family for their unwavering support, patience, and belief in me. Their encouragement and understanding have been the foundation of my academic and personal growth.

\noindent
This thesis is the culmination of the collective efforts of many individuals, and I sincerely appreciate everyone who has played a role in making this possible.

\vspace{1.5cm}
\noindent
\textbf{Onkar Phadtare} \\
\textit{FH Südwestfalen} \\
\textit{\today}

%=== END OF ACKNOWLEDGEMENT  ===
